### 2020-05-21 preface.tex
Mention the three volumes in preface
gathers -> gather
Fix paper count in preface
Oops :(
Add grant to preface

The proceedings contain papers that were accepted based on abstract submissions; each submission was thoroughly evaluated by three reviewers of our scientific board—for a full list of ECA committees, see www.ecargument.org. Volume I gathers 25 long papers and associated commentaries, together with 9 papers presented in the thematic panels that were held during ECA2019. Volume II gathers 67 regular papers that were presented during the conference.

Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings. First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality. In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants. Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these three volumes, and assisted us throughout in the process of producing the Proceedings.

>>>>

The proceedings contain papers that were accepted based on abstract submissions; each submission was thoroughly evaluated by three reviewers of our scientific board—for a full list of ECA committees, see www.ecargument.org. Volume I gathers 25 long papers and associated commentaries, together with 9 papers presented in the thematic panels that were held during ECA2019. Volumes II and III gather 69 regular papers that were presented during the conference.

Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings. First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality. In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants. Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these three volumes, and assisted us throughout in the process of producing the Proceedings. Thanks also to the European Research Council for generously supporting the production of the Proceedings by means of grant ERC-17-CoG 771074 for the project `The Social Epistemology of Argumentation' (PI C. Dutilh Novaes).
